---
title: "Biomass_Statistics"
author: "Derek Newberger"
date: "9/28/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data}
CoverCropData <- read.csv("/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_Peach_Data/CC_Biomass_Data/CoverCropData.csv")
# str(CoverCropData)
```

```{r}
CropRotationBiomassData <- read.csv("/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_Peach_Data/CC_Biomass_Data/CropRotationBiomass.csv")
```

```{r}
CropHalfData <- read.csv("/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_Peach_Data/CC_Biomass_Data/CoverCrop_Half.csv")
```

```{r}
CoverCropDatreorder <- CoverCropData                                     # Replicate original data
CoverCropDatreorder$Crop_Soil <- factor(CoverCropDatreorder$Crop_Soil,   # Change order manually
                  levels = c("Alfalfa_Autoclaved","Alfalfa","Fescue_Autoclaved","Fescue","Corn_Autoclaved","Corn","Tomato_Autoclaved", "Tomato", "None_Autoclaved", "None"))
```

```{r}
XSoillabs <- c("Autoclaved", "Control")
XCoverCroplabs <- c("Alfalfa Autoclaved","Alfalfa ","Fescue Autoclaved","Fescue","Corn Autoclaved","Corn","Tomato Autoclaved", "Tomato", "No Crop Autoclaved", "No Crop")
```

```{r}
library(ggplot2)
library(reshape2)
library(tidyverse)
library(emmeans)
library(ggthemes)
library(multcompView)
library(dplyr)
```

# Assumption Checks 

For an ANOVA we need homogenous variance. The most common way to check is to use the 'plot()' function. 

If your data are not normal/have heterogenous variance, then we need to transform the data. 

The most common transformation is a log transformation, there's also square root, ln, cubic, etc. If you are stuck finding an appropriate transformaion, use the box cox method. This test finds a multiplier that will make your data most fit the assumptions of an ANOVA. Whatever assumption you use, be sure to include in your manuscript. 

If there is no good fit to transform the data cleanly, consider non parametric methods of analysis. For an ANVOA analog, use the Kruskal Wallis test with the appropriate multiple comparison analog.

```{r}
lm_CropBiomass <- lm(Above_Biomass_g ~ Crop * Soil, data = CropRotationBiomassData) # soil treatment
plot(lm_CropBiomass)
```
```{r}
summary(lm_CropBiomass) #look at factor and level in R to change the reference 
```
From Stats lab:

You can also look at https://www.geeksforgeeks.org/specify-reference-factor-level-in-linear-regression-in-r/#:~:text=The%20relevel()%20function%20is%20used%20to%20reorder%20the%20factor,level%20set%20by%20the%20user

https://www.geeksforgeeks.org/specify-reference-factor-level-in-linear-regression-in-r/#:~:text=The%20relevel()%20function%20is%20used%20to%20reorder%20the%20factor,level%20set%20by%20the%20user

```{r}
lm_log_transformed_CropBiomass <- lm(log(Above_Biomass_g) ~ Crop * Soil, data = CropRotationBiomassData)
plot(lm_log_transformed_CropBiomass)
```

```{r}
lm_sqrt_transformed_CropBiomass <- lm(sqrt(Above_Biomass_g) ~ Soil * Crop, data = CropRotationBiomassData)
plot(lm_sqrt_transformed_CropBiomass)
```

```{r}
shapiro.test(residuals(lm_CropBiomass))
plot(lm_CropBiomass)
```
```{r}
shapiro.test(residuals(lm_log_transformed_CropBiomass))
plot(lm_log_transformed_CropBiomass)
```


```{r}
shapiro.test(residuals(lm_sqrt_transformed_CropBiomass))
plot(lm_sqrt_transformed_CropBiomass)
```

```{r, warning=F}
hist(residuals(lm_CropBiomass))
```
```{r}
hist(residuals(lm_sqrt_transformed_CropBiomass))
```

```{r}
lm_Biomass <- lm(Peach_Dry_Total ~ Soil * Crop, data = CoverCropData)
plot(lm_Biomass)
```

```{r}
lm_log_transformed_Biomass <- lm(log(Peach_Dry_Total) ~ Soil + Crop, data = CoverCropData)
plot(lm_log_transformed_Biomass)
```

```{r}
lm_sqrt_transformed_Biomass <- lm(sqrt(Peach_Dry_Total) ~ Soil + Crop, data = CoverCropData)
plot(lm_sqrt_transformed_Biomass)
```

```{r}
shapiro.test(residuals(lm_Biomass))
plot(lm_Biomass)
```

```{r}
shapiro.test(residuals(lm_log_transformed_Biomass))
plot(lm_log_transformed_Biomass)
```

```{r}
shapiro.test(residuals(lm_sqrt_transformed_Biomass))
plot(lm_sqrt_transformed_Biomass)
```

```{r, warning=F}
hist(residuals(lm_Biomass))
```

```{r}
hist(residuals(lm_log_transformed_Biomass))
```

```{r}
hist(residuals(lm_sqrt_transformed_Biomass))
```

```{r}
kruskal.test(Above_Biomass_g ~ Soil, data = CoverCropData)
kruskal.test(Peach_Dry_Total ~ Soil, data = CoverCropData)
```

```{r}
pairwise.wilcox.test(CropRotationBiomassData$Above_Biomass_g, CropRotationBiomassData$Crop_Soil,
                 p.adjust.method = "BH")
```

```{r CoverCropBiomassTreatment}
# analysis of variance
anovaDisruptionCC <- aov(Above_Biomass_g ~ Crop_Soil, data = CoverCropDatreorder)
```
```{r}
# Tukey's test
tukeyDisruptionCC <- TukeyHSD(anovaDisruptionCC)
```
```{r}
# compact letter display
cldDisruptionCC <- multcompLetters4(anovaDisruptionCC, tukeyDisruptionCC)
```
```{r}
# table with factors and 3rd quantile
dtDisruptionCC <- group_by(CoverCropDatreorder, Crop_Soil) %>%
  summarise(w=mean(Above_Biomass_g), sd = sd(Above_Biomass_g)) %>%
  arrange(desc(w))
```
```{r}
# extracting the compact letter display and adding to the Tk table
cldDisruptionCC <- as.data.frame.list(cldDisruptionCC$Crop_Soil)
dtDisruptionCC$cldDisruptionCC <- cldDisruptionCC$Letters
```
```{r}
print(dtDisruptionCC)
```
```{r}
p.vals <- pairwise.wilcox.test(CropRotationBiomassData$Above_Biomass_g, CropRotationBiomassData$Crop_Soil,
                 p.adjust.method = "BH")

mat <- as.matrix(p.vals$p.value)
myNames <- colnames(mat)
myNames <- c(myNames, 'Alfalfa_disrupted')

row1 <- rep(NA, 9)
mat <- rbind(row1, mat)
col1 <- rep(NA,10)
mat <- cbind(mat, col1)
colnames(mat) <- myNames
row.names(mat) <- myNames

#row.names(mat) <- c('', myNames)
res <- multcompView::multcompLetters(mat)
print(res)
```

```{r}
BiomassCC <-ggplot(subset(dtDisruptionCC, Crop_Soil %in% c("Alfalfa", "Alfalfa_Autoclaved", "Fescue", "Fescue_Autoclaved", "Corn", "Corn_Autoclaved", "Tomato", "Tomato_Autoclaved" )), aes(Crop_Soil, w, fill = Crop_Soil)) +
  geom_bar(stat = "identity") +
    scale_fill_manual(labels=c('Alfalfa Autoclaved', 'Alfalfa','Fescue Autoclaved', 'Fescue', 'Corn Autoclaved', 'Corn', 'Tomato Autoclaved', 'Tomato'), 
                      values = c("Alfalfa" = "darkorchid1",
                               "Alfalfa_Autoclaved" = "darkorchid4",
                               "Fescue" = "chartreuse",
                               "Fescue_Autoclaved" = "chartreuse4",
                               "Corn" = "gold",
                               "Corn_Autoclaved" = "gold4",
                               "Tomato" = "firebrick1",
                               "Tomato_Autoclaved" = "firebrick4")) +
  geom_errorbar(aes(ymin = w-sd, ymax=w+sd), width = 0.2) +
  labs(x = "Soil Treatment", y = "Mean Fresh Above Biomass (g)") +
  # geom_text(aes(label = cldDisruptionCC), vjust = -0.5, hjust = -0.5) +
  theme_few() +
  # ggtitle("Cover Crop Above Fresh Biomass") + 
  labs(fill='Crop History') +
  theme(plot.title = element_text(size=22)) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=12, face="bold")) +
  scale_x_discrete(labels= XCoverCroplabs) +
  theme(axis.title=element_text(size=14,face="bold"))
BiomassCC
  ggsave(BiomassCC, file='/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_R_Auto_Output/BarplotBiomassCC.pdf', width=10, height=4.6)
```


# analysis of variance
anovaDisruptionCRLog <- aov(Above_Biomass_Log ~ Crop_Soil, data = CropRotationBiomassData)

# Tukey's test
tukeyDisruptionCRLog <- TukeyHSD(anovaDisruptionCRLog)

# compact letter display
cldDisruptionCRLog <- multcompLetters4(anovaDisruptionCRLog, tukeyDisruptionCRLog)

# table with factors and 3rd quantile
dtDisruptionCRLog <- group_by(CropRotationBiomassData, Crop_Soil) %>%
  summarise(w=mean(Above_Biomass_Log), sd = sd(Above_Biomass_Log)) %>%
  arrange(desc(w))

# extracting the compact letter display and adding to the Tk table
cldDisruptionCRLog <- as.data.frame.list(cldDisruptionCRLog$Crop_Soil)
dtDisruptionCRLog$cldDisruptionCRLog <- cldDisruptionCRLog$Letters

print(dtDisruptionCRLog)


ggplot(subset(dtDisruptionCRLog, Crop_Soil %in% c("Alfalfa_Autoclaved", "Alfalfa", "Fescue_Autoclaved", "Fescue", "Corn_Autoclaved", "Corn", "Tomato_Autoclaved", "Tomato" )), aes(Crop_Soil, w, fill = Crop_Soil)) +
  geom_bar(stat = "identity") +
    scale_fill_manual(labels=c('Alfalfa Autoclaved', 'Alfalfa','Fescue Autoclaved', 'Fescue', 'Corn Autoclaved', 'Corn', 'Tomato Autoclaved', 'Tomato'), 
                      values = c("Alfalfa" = "darkorchid1",
                               "Alfalfa_Autoclaved" = "darkorchid4",
                               "Fescue" = "chartreuse",
                               "Fescue_Autoclaved" = "chartreuse4",
                               "Corn" = "gold",
                               "Corn_Autoclaved" = "gold4",
                               "Tomato" = "firebrick1",
                               "Tomato_Autoclaved" = "firebrick4")) +
  geom_errorbar(aes(ymin = w-sd, ymax=w+sd), width = 0.2) +
  labs(x = "Soil Treatment", y = "Mean Fresh Above Biomass (g)") +
  # geom_text(aes(label = cldDisruptionCC), vjust = -0.5, hjust = -0.5) +
  theme_few() +
  # ggtitle("Cover Crop Above Fresh Biomass") + 
  labs(fill='Crop History') +
  theme(plot.title = element_text(size=22)) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=12, face="bold")) +
  scale_x_discrete(labels= XCoverCroplabs) +
  theme(axis.title=element_text(size=14,face="bold"))


```{r PTotalDry}
# analysis of variance
anovaPTotalDry <- aov(Peach_Dry_Total ~ Crop_Soil, data = CoverCropData)
```
```{r}
# Tukey's test
tukeyPTotalDry <- TukeyHSD(anovaPTotalDry)
```
```{r}
# compact letter display
cldPTotalDry <- multcompLetters4(anovaPTotalDry, tukeyPTotalDry)
```
```{r}
# table with factors and 3rd quantile
dtPTotalDry <- group_by(CoverCropData, Crop_Soil) %>%
  summarise(w=mean(Peach_Dry_Total), sd = sd(Peach_Dry_Total)) %>%
  arrange(desc(w))
```
```{r}
# extracting the compact letter display and adding to the Tk table
cldPTotalDry <- as.data.frame.list(cldPTotalDry$Crop_Soil)
dtPTotalDry$cldPTotalDry <- cldPTotalDry$Letters
```
```{r}
print(dtPTotalDry)
```

```{r}
p.valsPeach <- pairwise.wilcox.test(CoverCropData$Peach_Dry_Total, CoverCropData$Crop_Soil,
                 p.adjust.method = "BH")

mat <- as.matrix(p.valsPeach$p.value)
myNames <- colnames(mat)
myNames <- c(myNames, 'Tomato_disrupted')

row1 <- rep(NA, 9)
mat <- rbind(row1, mat)
col1 <- rep(NA,10)
mat <- cbind(mat, col1)
colnames(mat) <- myNames
row.names(mat) <- myNames

#row.names(mat) <- c('', myNames)
resPeach <- multcompView::multcompLetters(mat)
print(resPeach)
```

```{r}
dtPTotalDryreorder <- dtPTotalDry                                    # Replicate original data
dtPTotalDryreorder$Crop_Soil <- factor(dtPTotalDryreorder$Crop_Soil,   # Change order manually
                  levels = c("Alfalfa_Autoclaved","Alfalfa","Fescue_Autoclaved","Fescue","Corn_Autoclaved","Corn","Tomato_Autoclaved", "Tomato", "None_Autoclaved", "None"))

BiomassP <-ggplot(dtPTotalDryreorder, aes(Crop_Soil, w, fill = Crop_Soil)) +
  #geom_bar(stat = "identity", aes(fill = w), show.legend = FALSE) +
    geom_bar(stat = "identity") +
    scale_fill_manual(labels=c('Alfalfa Autoclaved', 'Alfalfa','Fescue Autoclaved', 'Fescue', 'Corn Autoclaved', 'Corn', 'Tomato Autoclaved', 'Tomato', 'No Crop Autoclaved', 'No Crop'), values = c("Alfalfa" = "darkorchid1",
                               "Alfalfa_Autoclaved" = "darkorchid4",
                               "Fescue" = "chartreuse",
                               "Fescue_Autoclaved" = "chartreuse4",
                               "Corn" = "gold",
                               "Corn_Autoclaved" = "gold4",
                               "Tomato" = "firebrick1",
                               "Tomato_Autoclaved" = "firebrick4",
                               "None" = "grey69",
                               "None_Autoclaved" = "grey49")) +
  geom_errorbar(aes(ymin = w-sd, ymax=w+sd), width = 0.2) +
  labs(x = "Crop and Soil Treatment", y = "Mean Biomass (g)") +
  # geom_text(aes(label = cldPTotalDry), vjust = -0.5, hjust = -0.5) +
  theme_few() +
  ylim(0,7) +
  # ggtitle("Total Dry Peach Biomass") + 
  labs(fill='Crop History') +
    # geom_text(aes(label = cldPTotalDry), vjust = -0.5, hjust = -0.5) +
  theme(plot.title = element_text(size=22)) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=12, face="bold")) +
  scale_x_discrete(labels= XCoverCroplabs) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
BiomassP
  ggsave(BiomassP, file='/Users/derek_newberger/Desktop/Thesis_CSU/Cover_Crop_Peach/CC_R_Auto_Output/BarplotBiomassP.pdf', width=11.5, height=4.6)
```

```{r}
pairwise.wilcox.test(CoverCropData$Peach_Dry_Total, CoverCropData$Crop_Soil,
                 p.adjust.method = "BH")
```

```{r}
pairwise.wilcox.test(CropHalfData$Peach_Dry_Total, CropHalfData$Crop,
                 p.adjust.method = "BH")
```


```{r PTotalDry}
# analysis of variance
anovaPHeight <- aov(Peach_Tree_Height_Difference ~ Crop_Soil, data = CoverCropData)
```
```{r}
# Tukey's test
tukeyPHeight <- TukeyHSD(anovaPHeight)
```
```{r}
# compact letter display
cldPHeight <- multcompLetters4(anovaPHeight, tukeyPHeight)
```
```{r}
# table with factors and 3rd quantile
dtPHeight <- group_by(CoverCropData, Crop_Soil) %>%
  summarise(w=mean(Peach_Tree_Height_Difference), sd = sd(Peach_Tree_Height_Difference)) %>%
  arrange(desc(w))
```
```{r}
# extracting the compact letter display and adding to the Tk table
cldPHeight <- as.data.frame.list(cldPHeight$Crop_Soil)
dtPHeight$cldPHeight <- cldPHeight$Letters
```
```{r}
print(dtPHeight)
```

```{r}
dtPHeightreorder <- dtPHeight                                    # Replicate original data
dtPHeightreorder$Crop_Soil <- factor(dtPHeightreorder$Crop_Soil,   # Change order manually
                  levels = c("Alfalfa_Autoclaved","Alfalfa","Fescue_Autoclaved","Fescue","Corn_Autoclaved","Corn","Tomato_Autoclaved", "Tomato", "None_Autoclaved", "None"))

ggplot(dtPHeightreorder, aes(Crop_Soil, w, fill = Crop_Soil)) +
  #geom_bar(stat = "identity", aes(fill = w), show.legend = FALSE) +
    geom_bar(stat = "identity") +
    scale_fill_manual(labels=c('Alfalfa Autoclaved', 'Alfalfa','Fescue Autoclaved', 'Fescue', 'Corn Autoclaved', 'Corn', 'Tomato Autoclaved', 'Tomatod', 'No Crop Autoclaved', 'No Crop'), values = c("Alfalfa" = "darkorchid1",
                               "Alfalfa_Autoclaved" = "darkorchid4",
                               "Fescue" = "chartreuse",
                               "Fescue_Autoclavedd" = "chartreuse4",
                               "Corn" = "gold",
                               "Corn_Autoclaved" = "gold4",
                               "Tomato" = "firebrick1",
                               "Tomato_Autoclaved" = "firebrick4",
                               "None" = "grey69",
                               "None_Autoclaved" = "grey49")) +
  geom_errorbar(aes(ymin = w-sd, ymax=w+sd), width = 0.2) +
  labs(x = "Crop and Soil Treatment", y = "Height Difference (Final- Initial) (cm)") +
  geom_text(aes(label = cldPHeight), vjust = -0.5, hjust = -0.5) +
  theme_few() +
  # ggtitle("Height Difference After 12? weeks") + 
  labs(fill='Crop History') +
  theme(plot.title = element_text(size=22)) +
  theme(axis.text.x = element_text(angle = 45, hjust=1, size=12, face="bold")) +
  scale_x_discrete(labels= XCoverCroplabs) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold"))
```